---
title: "German Bank"
author: "Leandro Sampaio"
date: "August 18, 2018"
output: html_document
---

```{r}
suppressMessages(if(!require(ggplot2)){install.packages("ggplot2")})
suppressMessages(if(!require(GGally)){install.packages("GGally")})
suppressMessages(if(!require(psci)){install.packages("psci")})

suppressMessages(if(!require(broom)){install.packages("broom")})
suppressMessages(if(!require(tidyverse)){install.packages("tidyverse")})

suppressMessages(if(!require(scales)){install.packages("scales")})
suppressMessages(if(!require(ggthemes)){install.packages("ggthemes")})
suppressMessages(if(!require(dplyr)){install.packages("dplyr")})
suppressMessages(if(!require(randomForest)){install.packages("randomForest")})
suppressMessages(if(!require(corrplot)){install.packages("corrplot")})
suppressMessages(if(!require(plyr)){install.packages("plyr")})

theme_set(theme_bw())

dataset<-read.csv("dataset/german.csv", header = TRUE, sep = ";", dec=",");

str(dataset_test)

names(dataset) <- tolower(names(dataset)); str(dataset)
dataset$obs.<-NULL
str(dataset)

#transforma em fatores as variáveis categóricas e "dummies"
dataset[,"chk_acct"] <- as.factor(dataset[,"chk_acct"])
dataset[,"history"] <- as.factor(dataset[,"history"])
dataset[,"new_car"] <- as.factor(dataset[,"new_car"])
dataset[,"used_car"] <- as.factor(dataset[,"used_car"])
dataset[,"furniture"] <- as.factor(dataset[,"furniture"])
dataset[,"radio.tv"] <- as.factor(dataset[,"radio.tv"])
dataset[,"education"] <- as.factor(dataset[,"education"])
dataset[,"retraining"] <- as.factor(dataset[,"retraining"])
dataset[,"sav_acct"] <- as.factor(dataset[,"sav_acct"])
dataset[,"employment"] <- as.factor(dataset[,"employment"])
dataset[,"male_div"] <- as.factor(dataset[,"male_div"])
dataset[,"male_single"]  <- as.factor(dataset[,"male_single"])
dataset[,"co.applicant"]  <- as.factor(dataset[,"co.applicant"])
dataset[,"guarantor"] <- as.factor(dataset[,"guarantor"])
dataset[,"real_estate"]  <- as.factor(dataset[,"real_estate"])
dataset[,"other_install"] <- as.factor(dataset[,"other_install"])
dataset[,"rent"] <- as.factor(dataset[,"rent"])
dataset[,"own_res"] <- as.factor(dataset[,"own_res"])
dataset[,"num_credits"]  <- as.factor(dataset[,"num_credits"])
dataset[,"job"] <- as.factor(dataset[,"job"])
dataset[,"telephone"] <- as.factor(dataset[,"telephone"])
dataset[,"foreign"] <- as.factor(dataset[,"foreign"])
#variável dependente
dataset[,"response"]  <- as.factor(dataset[,"response"])
#transforma em numeric
dataset[,"amount"] <- as.numeric(dataset[,"amount"])
dataset[,"install_rate"] <- as.numeric(dataset[,"install_rate"])
dataset[,"age"] <- as.numeric(dataset[,"age"])
dataset[,"duration"]  <- as.numeric(dataset[,"duration"])
```

Codelist				
Var. #	Variable Name	Description	Variable Type	Code Description
				
1.  OBS#	    Observation No.	Categorical	
2. 	CHK_ACCT	Checking account status	Categorical	0 : < 0 DM
				1:  0 < ...< 200 DM
				2 : => 200 DM
				3:  no checking account
3. 	DURATION	Duration of credit in months	Numerical	
4. 	HISTORY	    Credit history	Categorical	0: no credits taken                                                                                                                   
				1: all credits at this bank paid back duly 
				2: existing credits paid back duly till now 
				3: delay in paying off in the past  
				4: critical account  
5. 	NEW_CAR	    Purpose of credit	Binary	car (new)   0: No, 1: Yes
6.	USED_CAR	Purpose of credit	Binary	car (used)    0: No, 1: Yes
7.	FURNITURE	Purpose of credit	Binary	furniture/equipment    0: No, 1: Yes
8.	RADIO/TV	Purpose of credit	Binary	radio/television    0: No, 1: Yes
9.	EDUCATION	Purpose of credit	Binary	education    0: No, 1: Yes
10.	RETRAINING	Purpose of credit	Binary	retraining    0: No, 1: Yes
11.	AMOUNT	    Credit amount	Numerical	
12.	SAV_ACCT	Average balance in savings account	Categorical	0 : <  100 DM
				1 : 100<= ... <  500 DM
				2 : 500<= ... < 1000 DM
				3 : =>1000 DM
				4 :   unknown/ no savings account
13.	EMPLOYMENT	Present employment since	Categorical	0 : unemployed
				1:  < 1 year
				2 : 1 <= ... < 4 years  
				3 : 4 <=... < 7 years
				4 : >= 7 years
14.	INSTALL_RATE	Installment rate as % of disposable income	Numerical	
15.	MALE_DIV	Applicant is male and divorced	Binary	 0: No, 1: Yes
16.	MALE_SINGLE	Applicant is male and single	Binary	 0: No, 1: Yes
17.	MALE_MAR_WID	Applicant is male and married or a widower	Binary	 0: No, 1: Yes
18.	CO-APPLICANT	Application has a co-applicant	Binary	 0: No, 1: Yes
19.	GUARANTOR	Applicant has a guarantor	Binary	 0: No, 1: Yes
20.	PRESENT_RESIDENT	Present resident since - years	Categorical	0: <= 1 year
				1<…<=2 years
				2<…<=3 years
				3:>4years
21.	REAL_ESTATE	Applicant owns real estate	Binary	 0: No, 1: Yes
22.	PROP_UNKN_NONE	Applicant owns no property (or unknown)	Binary	 0: No, 1: Yes
23.	AGE	Age in years	Numerical	
24.	OTHER_INSTALL	Applicant has other installment plan credit	Binary	 0: No, 1: Yes
25.	RENT	Applicant rents 	Binary	 0: No, 1: Yes
26.	OWN_RES	Applicant owns residence	Binary	 0: No, 1: Yes
27.	NUM_CREDITS	Number of existing credits at this bank	Numerical	
28.	JOB	Nature of job	Categorical	0 : unemployed/ unskilled  - non-resident
				1 : unskilled - resident
				2 : skilled employee / official
				3 : management/ self-employed/highly qualified employee/ officer
29.	NUM_DEPENDENTS	Number of people for whom liable to provide maintenance	Numerical	
30.	TELEPHONE	Applicant has phone in his or her name	Binary	 0: No, 1: Yes
31.	FOREIGN	Foreign worker	Binary	 0: No, 1: Yes
32.	RESPONSE	Credit rating is good	Binary	 0: No, 1: Yes


```{r}
#Índices obtidos após a aleatorização
srt <- sort(sample(nrow(dataset), nrow(dataset)*.6))
#Dados para o treinamento
training <- dataset[srt,]
#Dados para a validação
test <- dataset[-srt,]
```


```{r}
mod.full <- glm(response ~ . ,family=binomial(),data=training);summary(mod.full)
#Abordagem Stepwise para seleção de variáveis
stepwise <- step(mod.full,direction="both");summary(stepwise)

mod.optimize <- glm(family=binomial(),data=training
    ,response ~ chk_acct + duration + history + new_car + used_car + 
    education + amount + sav_acct + install_rate + male_single + 
    guarantor + age + other_install)
summary(mod.optimize)
#Calcula a razão de chances
exp(cbind(OR = coef(stepwise), confint(stepwise)))
```